Capitalized Title Here

### 2021-03-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
step by step instructions

In the example in section "Implementation" we would see that, two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y. We also implemented graphing tools for users to better understand these results as well as the algorithm itself.

@@

The CMPS algorithm consists of X steps.

step 1) cut the reference profile into consecutive, non-overlapping and equal-length basis segments;

`get_segs(x, len=50)` implements the first step. It takes a profile in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.

step 2) each basis segment finds its best registration position on the comparison profile. A cross-correlation curve between a basis segment and the comparison profile would be computed, and a registration position is considered as "good" if the basis segment achieves a high cross-correlation value at this position.

Then how should a basis segment find its best registration position? [In the original paper] researchers proposed two versions of the CMPS alrorithm that can answer this question. The first version is called "multi-peak inspection", and the second version is called "multi-peak inspection at different segment lengths/scales". We also refer the second version as the CMPS algorithm using "the multi segment lengths strategy".

Step 2.1) multi-peak inspection: each basis segment identifies positions of 5 (or multiple) highest peaks in the cross-correlation curve. Since false positive peaks would stand out when the segment length is short, positions of all 5 peak will be considered as the potential "best" registration position.

Step 2.2) multi segment lengths strategy: for this version of the CMPS algorithm, each basis segment finds only one "best" registration position. This "best" registration position can be found by conducting multi-peak inspection multiple rounds. The first round is the standard way as we have stated in step 2.1. But after the first round, we will increase the segment length, compute a new cross-correlation curve, and again identify multiple peaks in the cross-correlation curve. The number of peaks identified in this round is typically less than that in the previous round (say 3 highest peaks) since increasing the segment length can reduce the number of false positive peaks. We can repeat this procedure multiple times; however in the last round, only one highest peak should be identified. If a position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).

>>>>

\hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}

In the example in section "Implementation" we  see that two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y. We also implemented graphing tools for users to better understand these results as well as the algorithm itself.

@@

The CMPS algorithm consists of \hh{three main} steps:

1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
the command `get_segs(x, len=50)` implements this first step. 
It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.

2. **register each basis segment on the comparison profile:** 
Calculate the cross-correlation curve between a basis segment and the comparison profile.A registration position is considered as "good" if the basis segment achieves a high cross-correlation value at that position. 
The best registration position is decided upon using  a multi-peak inspection with or without different segment lengths:

    2.1. **multi-peak inspection (without different segment lengths):** each basis segment identifies positions of 5 (or multiple) highest peaks in the cross-correlation curve. Since false positive peaks would stand out when the segment length is short, positions of all 5 peak will be considered as the potential "best" registration position.

    2.2. **multi-peak inspection with different segment lengths:** for this version of the CMPS algorithm, each basis segment finds only one "best" registration position. This "best" registration position can be found by conducting multi-peak inspection multiple rounds. The first round is the standard way as we have stated in step 2.1. But after the first round, we will increase the segment length, compute a new cross-correlation curve, and again identify multiple peaks in the cross-correlation curve. The number of peaks identified in this round is typically less than that in the previous round (say 3 highest peaks) since increasing the segment length can reduce the number of false positive peaks. We can repeat this procedure multiple times; however in the last round, only one highest peak should be identified. If a position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).
